Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-10 exp1/iswc2013.tex
wrong university name
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@576 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{Introducing Statistical Design of Experiments to SPARQL
  Endpoint Evaluation}
\author{Kjetil Kjernsmo\inst{1} \and John S. Tyssedal\inst{2}}
\titlerunning{Introducing Design of Experiments to SPARQL Evaluation}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjekje@ifi.uio.no} \and Department of Mathematical Sciences,
The Norwegian Institute of Technology,
N-7491 Trondheim,
Norway
\email{john.tyssedal@math.ntnu.no}}

>>>>

\title{Introducing Statistical Design of Experiments to SPARQL
  Endpoint Evaluation}
\author{Kjetil Kjernsmo\inst{1} \and John S. Tyssedal\inst{2}}
\titlerunning{Introducing Design of Experiments to SPARQL Evaluation}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjekje@ifi.uio.no} \and Department of Mathematical Sciences,
Norwegian University of Science and Technology,
N-7491 Trondheim,
Norway
\email{john.tyssedal@math.ntnu.no}}
